Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Updated Model

library(tidyverse)
library(palmerpenguins)
```

@@

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

@@

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

@@

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

@@

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

>>>>

library(tidyverse)
```

@@

The dataset used for this analysis was sourced from FiveThirtyEight’s poll aggregation platform, which compiles high-quality polling data from various reputable pollsters across the U.S. (@fivethirtyeight). This analysis uses the statistical programming language R (@R) and various libraries for data manipulation and visualization, including tidyverse for efficient data wrangling and ggplot2 for creating insightful visualizations (@tidyverse, @ggplot2). By employing robust statistical methods and tools, this analysis seeks to forecast potential outcomes of the 2024 U.S. Presidential Election.

@@

@@

In this analysis, the outcome variable of interest is the percentage of support a candidate receives in each poll, represented by pct. This variable indicates the proportion of respondents within a poll who favor a particular candidate, measured as a percentage. Given that pct serves as a continuous variable bounded between 0 and 100, it is well-suited for modeling the levels of support across different polls and over time.

@@

This analysis employs two predictive models to estimate the anticipated support for the two major candidates in the 2024 U.S. Presidential Election: a multiple linear regression model. These models use high-quality polling data from reputable sources, with relevant predictors to provide insights into public opinion trends.

@@

The multiple linear regression model is designed to predict the candidate's percentage of support (pct) as a linear function of various predictors. Formally, we define the model as:

\begin{align*}
\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{sample\_size}_i + \beta_3 \cdot \text{transparency\_score}_i \\
&\quad + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_4 \cdot \text{end\_date}_i + \epsilon_i,
\end{align*}
